<<<<<<< HEAD
---
title: "Untitled"
author: "Mariana_euan"
date: "`r Sys.Date()`"
output: html_document
---
# Mariana Euan 

Here is my website. 

**[cv](http://EuanisMariana8082.io/

<<<<<<< HEAD
---
title: "Euan_"
author: "Mariana_euan"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```





```{r pressure, echo=FALSE}
plot(pressure)
```
=======
---
title: "Euan_"
author: "Mariana_euan"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```





```{r pressure, echo=FALSE}
plot(pressure)
```

```{r echo=FALSE}
knitr::include_graphics("./media/download(11)/png")
```

[Home](http://EuanisMariana8082.github.io/) |[About Me](http://EuanisMariana8082.github.io/about-me)

[CV](http://EuanisMariana8082.github.io/My_Resume_of_2023.csv)
 
#index.Rmd
# add a cv file
# is -l 


=======
---
title: "Untitled"
author: "Mariana_euan"
date: "`r Sys.Date()`"
output: html_document
---
# Mariana Euan 

Here is my website. 

**[cv](http://EuanisMariana8082.io)



```{r echo=FALSE}
knitr::include_graphics("./media/burger/png")
```

[Home](http://EuanisMariana8082.github.io/) |[About Me](http://EuanisMariana8082.github.io/about-me)
[CV]

#index.Rmd
# add a cv file
# is -l 

