---
title: "Exploring Bad Bunny’s Musical Journey: Spotify Streams and Collaborations"
author: "Mariana_Euan"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

<style>
body {
  font-family: 'Garamond', serif;
  background-color: #CEDBF0;
}
</style>



```{r load_data, echo = FALSE,warning = FALSE,message= FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message= FALSE)
library(hrbrthemes)
library(ggplot2)
library(gganimate)
library(wordcloud)
library(maps)
library(mapdata)
file_path <- "C:/Users/Rushe/EuanisMariana8082.github.io/My_Final_Project/UVST_ALBUM.csv"
UVST_ALBUM <- read.csv(file_path)
UVST_ALBUM$Plays <- as.numeric(gsub(",", "", UVST_ALBUM$Plays))
```


# scatter plot 

# Un Verano Sin Ti
This scatter plot is looking at Uno Verano Sin Ti streams from Spotify. 
Based on the scatter plot of the song “Un Verano Sin Ti” by Bad Bunny on Spotify, here are some observations:

The song has been streamed between 400,000 and 1,600,000 times.
The highest number of streams appears to be in the Callaita. 
The lowest number of streams appears to be in the “El Apagon
The scatter plot shows a wide range of streams across different categories, indicating a diverse listener base for this song.
```{r scatter_plot, echo = FALSE,warning = FALSE,message= FALSE}
# Reorder factor levels
UVST_ALBUM$Song.Name <- factor(UVST_ALBUM$Song.Name, levels = UVST_ALBUM$Song.Name[order(UVST_ALBUM$Plays)])

# Plot
ggplot(UVST_ALBUM, aes(x = Song.Name, y = Plays)) +
  geom_point(size = 2) +  # Increase the size of the dots
  scale_y_continuous(labels = scales::comma) +  # Format y-axis labels
  theme_bw() +
  theme(panel.grid.major = element_line(size = 1.5, color = "#C8E6BD"),
        panel.grid.minor = element_line(size = 1.5, color = "#F8C8CA"),
        axis.text.x = element_text(angle = 90, vjust = 2.0, hjust=1))  # Rotate x-axis labels


```


# Nadie Sabe Lo Que Va a Pasar Mañana Streams on Spotify
 Most streamed so far is Where She Goes. Most of the songs seemed to be at the same level for streaming. It was released on October 13, 2023 so it hasn't been out for long.

```{r scatter_NSLQVPM, echo = FALSE,warning = FALSE,message= FALSE}
# Load necessary libraries
library(ggplot2)
library(scales)

# Read the file
NSLQVAPM_ALBUM <- read.csv("C:\\Users\\Rushe\\EuanisMariana8082.github.io\\My_Final_Project\\NSLQVAPM_ALBUM.csv")

# Convert plays to numeric
NSLQVAPM_ALBUM$Plays <- as.numeric(gsub(",", "", NSLQVAPM_ALBUM$Plays))

# Reorder the levels of Name.of.Song based on Plays
NSLQVAPM_ALBUM$Name.of.Song <- factor(NSLQVAPM_ALBUM$Name.of.Song, levels = NSLQVAPM_ALBUM$Name.of.Song[order(NSLQVAPM_ALBUM$Plays)])

# Create a scatter plot
ggplot(NSLQVAPM_ALBUM, aes(x = Name.of.Song, y = Plays)) +
  geom_point(size = 4) +  # Increase the size of the points
  scale_y_continuous(labels = scales::comma) +  # Format y-axis labels
  theme_bw() +
  theme(panel.grid.major = element_line(size = 2.5, color = "#FFE4CD"),
        panel.grid.minor = element_line(size = 2.3, color = "#D9E6F7"),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  # Rotate x-axis text


```

# Word Cloud 


 Un Verano Sin Ti Name of Songs

```{r word_cloud, echo = FALSE,warning = FALSE,message= FALSE}
wordcloud(words = UVST_ALBUM$Song.Name, freq = UVST_ALBUM$Plays, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=c("#FFC5D0", "#9AE1E1", "#F4C6EF"))
```
 
 
Nadie Sabe Lo Que Va a Pasar Mañana  Name of Songs 

```{r word_cloud_2, echo = FALSE,warning = FALSE,message= FALSE}
# Load necessary libraries
library(wordcloud)
library(RColorBrewer)

# Read the file
NSLQVAPM_ALBUM <- read.csv("C:\\Users\\Rushe\\EuanisMariana8082.github.io\\My_Final_Project\\NSLQVAPM_ALBUM.csv")

# Convert plays to numeric
NSLQVAPM_ALBUM$Plays <- as.numeric(gsub(",", "", NSLQVAPM_ALBUM$Plays))

# Create a word cloud
wordcloud(words = NSLQVAPM_ALBUM$Name.of.Song, freq = NSLQVAPM_ALBUM$Plays, min.freq = 4,
          max.words=200, random.order=FALSE, rot.per=0.35, scale=c(1.5,1.5),
          colors=brewer.pal(8, "Dark2"))

```

# Map Plot 

```{r map_plot, echo = FALSE,warning = FALSE,message= FALSE}
# Data
artist_data <- data.frame(
  Artist_Name = c("Young Miko", "Mora", "Byrant Myers", "Luar La L", "Yovngchimi", "Eladio Carrion", "feid", "arcangel", "Rafael Castillo", "nengo flow"),
  monthly_listeners = c(30172477, 25268540, 16082345, 9006894, 10122460, 20951154, 44330186, 25869232, 18421243, 19617966),
  origin = c("Añasco, Puerto Rico", "Bayamón, Puerto Rico", "Carolina, Puerto Rico", "Carolina, Puerto Rico", "San Juan, Puerto Rico", "Kansas City, MO", "Medellín, Colombia", "East Harlem, New York", "The Bronx, New York", "San Juan, Puerto Rico"),
  Latitude = c(18.28273, 18.39856, 18.38078, 18.38078, 18.466333, 39.099724, 6.25184, 40.816357, 40.837048, 18.466333),
  Longitude = c(-67.13962, -66.15572, -65.95739, -65.95739, -66.105721, -94.578331, -75.56359, -73.962898, -73.865433, -66.105721)
)

# Capitalize artist names
artist_data$Artist_Name <- toupper(artist_data$Artist_Name)

# Get world map data
world_map <- map_data("world")

# Plot
ggplot() +
  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), fill = "#FFAEB9", color = "#3ABCBF") +
  geom_point(data = artist_data, aes(x = Longitude, y = Latitude, color = Artist_Name), size = 4) +
  coord_fixed(1.8) +
  scale_color_discrete(name = "Artist Name") +
  theme_minimal() +
  labs(x = "Longitude", y = "Latitude")  # Add this line to change the axis labels


```


This plot is a geographical representation of the origins of various artists. Each point on the map corresponds to an artist, and the location of the point indicates the origin of the artist. The artists represented in this plot include Young Miko, Mora, Byrant Myers, Luar La L, Yovngchimi, Eladio Carrion, Feid, Arcangel, Rafael Castillo, and Nengo Flow.

Here’s a more detailed breakdown:

Young Miko is from Añasco, Puerto Rico.
Mora is from Bayamón, Puerto Rico.
Byrant Myers is from Carolina, Puerto Rico.
Luar La L is also from Carolina, Puerto Rico.
Yovngchimi is from San Juan, Puerto Rico.
Eladio Carrion is from Kansas City, MO, United States.
Feid is from Medellín, Colombia.
Arcangel is from East Harlem, New York, United States.
Rafael Castillo is from The Bronx, New York, United States.
Nengo flow is from San Juan, Puerto Rico.

The color coding of the points allows us to distinguish between the artists. This plot provides a visual way to understand the geographical distribution of these artists’ origins. It shows that these artists come from diverse locations, with a concentration in the Americas. This diversity might be reflected in their music, influencing their style and the themes they explore.

#FFAEB9

#A8E1B7


```{r map_2, echo = FALSE,warning = FALSE,message= FALSE}
#

```

